### 2023-02-19 chapters/fairness/fvgm/appendix.tex
short captions
reference fixed

	\subsection{Accuracy Comparison Among Different Verifiers}
	We have considered a synthetic problem for comparing accuracy among different verifiers. For Example~\ref{fvgm_example:intro}, we consider `age $ \ge 40 $' as a Bernoulli random  variable with probability $ 0.5 $. For `income' feature ($ I $), we consider two Gaussian distributions $ \Pr[I | \text{age} \ge 40] \sim \mathcal{N}(0.6, 0.1) $ and $ \Pr[I | \text{age} < 40] \sim \mathcal{N}(0.4, 0.1) $ separated by two age groups. Moreover, for `fitness' feature ($ F $), we consider two Gaussian distributions $ \Pr[F | \text{age} \ge 40] \sim \mathcal{N}(0.7, 0.1) $ and $ \Pr[F | \text{age} < 40] \sim \mathcal{N}(0.3, 0.1) $. On this data, the trained LR and SVM classifier has decision boundary as $ 7.26I + 7.4F - 1.34A \ge 6.62 $ and $ 9.37I + 9.75F - 0.34A \ge 9.4 $, respectively.

@@

%			\subfloat{\includegraphics[scale=0.4]{figures/fairness/fvgm/time_vary_features_Ricci_LR}}
%			\subfloat{\includegraphics[scale=0.4]{figures/fairness/fvgm/time_vary_features_Ricci_SVM}}
%			
			\caption{Effect of number of features on the runtime of different datasets for LR and SVM classifiers.}
			\label{fairness_fvgm_fig:time_vary_features}

>>>>

	\subsection{Accuracy Comparison Among Different Verifiers}
	We have considered a synthetic problem for comparing accuracy among different verifiers. For Example~\ref{fairness_justicia_example:intro}, we consider `age $ \ge 40 $' as a Bernoulli random  variable with probability $ 0.5 $. For `income' feature ($ I $), we consider two Gaussian distributions $ \Pr[I | \text{age} \ge 40] \sim \mathcal{N}(0.6, 0.1) $ and $ \Pr[I | \text{age} < 40] \sim \mathcal{N}(0.4, 0.1) $ separated by two age groups. Moreover, for `fitness' feature ($ F $), we consider two Gaussian distributions $ \Pr[F | \text{age} \ge 40] \sim \mathcal{N}(0.7, 0.1) $ and $ \Pr[F | \text{age} < 40] \sim \mathcal{N}(0.3, 0.1) $. On this data, the trained LR and SVM classifier has decision boundary as $ 7.26I + 7.4F - 1.34A \ge 6.62 $ and $ 9.37I + 9.75F - 0.34A \ge 9.4 $, respectively.

@@

%			\subfloat{\includegraphics[scale=0.4]{figures/fairness/fvgm/time_vary_features_Ricci_LR}}
%			\subfloat{\includegraphics[scale=0.4]{figures/fairness/fvgm/time_vary_features_Ricci_SVM}}
%			
			\caption[Ablation study: effect of the number of features]{Effect of number of features on the runtime of different datasets for LR and SVM classifiers.}
			\label{fairness_fvgm_fig:time_vary_features}

### 2023-02-19 tables/fairness/fvgm/sanity_check.tex
reference fixed

	\caption{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on logistic regression classifier.}
	\label{fairness_fvgm_fig:synthetic_results}
\end{figure}

@@

	\caption{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on SVM classifier.}
	\label{fairness_fvgm_fig:synthetic_results_SVM}
\end{figure}

>>>>

	\caption[Accuracy of {\fvgm} on logistic regression classifier]{
		Measuring accuracy of different fairness verifiers for Example~\ref{fairness_justicia_example:intro} on logistic regression classifier.}
	\label{fairness_fvgm_fig:synthetic_results}
\end{figure}

@@

	\caption[Accuracy of {\fvgm} on SVM classifier]{
		Measuring accuracy of different fairness verifiers for Example~\ref{fairness_justicia_example:intro} on SVM classifier.}
	\label{fairness_fvgm_fig:synthetic_results_SVM}
\end{figure}
